---
title: "Getting Lyrics"
format: html
editor: visual
---

```{r}
library(geniusr)
library(tidyverse)
```

```{r}
genius_token()
```

-   [3D Na'Tee](https://en.wikipedia.org/wiki/3D_Na%27Tee "3D Na'Tee")

### **A**

-   [Aesja](https://en.wikipedia.org/wiki/Aesja "Aesja")

-   [Ai (singer)](https://en.wikipedia.org/wiki/Ai_(singer) "Ai (singer)")

-   [Ak'Sent](https://en.wikipedia.org/wiki/Ak%27Sent "Ak'Sent")

-   [Amil](https://en.wikipedia.org/wiki/Amil "Amil")

-   [Anquette](https://en.wikipedia.org/wiki/Anquette "Anquette")

-   [Antoinette (rapper)](https://en.wikipedia.org/wiki/Antoinette_(rapper) "Antoinette (rapper)")

-   [Aqsa (rapper)](https://en.wikipedia.org/wiki/Aqsa_(rapper) "Aqsa (rapper)")

-   [Whitney Avalon](https://en.wikipedia.org/wiki/Whitney_Avalon "Whitney Avalon")

-   [Awkwafina](https://en.wikipedia.org/wiki/Awkwafina "Awkwafina")

### **B**

-   [Apani B](https://en.wikipedia.org/wiki/Apani_B "Apani B")

-   [Bahamadia](https://en.wikipedia.org/wiki/Bahamadia "Bahamadia")

-   [Charli Baltimore](https://en.wikipedia.org/wiki/Charli_Baltimore "Charli Baltimore")

-   [Azealia Banks](https://en.wikipedia.org/wiki/Azealia_Banks "Azealia Banks")

-   [Dee Barnes](https://en.wikipedia.org/wiki/Dee_Barnes "Dee Barnes")

-   [BbyMutha](https://en.wikipedia.org/wiki/BbyMutha "BbyMutha")

-   [Big Boss Vette](https://en.wikipedia.org/wiki/Big_Boss_Vette "Big Boss Vette")

-   [Porcelain Black](https://en.wikipedia.org/wiki/Porcelain_Black "Porcelain Black")

-   [Toni Blackman](https://en.wikipedia.org/wiki/Toni_Blackman "Toni Blackman")

-   [Amanda Blank](https://en.wikipedia.org/wiki/Amanda_Blank "Amanda Blank")

-   [Bianca Bonnie](https://en.wikipedia.org/wiki/Bianca_Bonnie "Bianca Bonnie")

-   [Boss (rapper)](https://en.wikipedia.org/wiki/Boss_(rapper) "Boss (rapper)")

-   [Da Brat](https://en.wikipedia.org/wiki/Da_Brat "Da Brat")

-   [Bhad Bhabie](https://en.wikipedia.org/wiki/Bhad_Bhabie "Bhad Bhabie")

-   [Foxy Brown (rapper)](https://en.wikipedia.org/wiki/Foxy_Brown_(rapper) "Foxy Brown (rapper)")

-   [Dai Burger](https://en.wikipedia.org/wiki/Dai_Burger "Dai Burger")

-   [Kandi Burruss](https://en.wikipedia.org/wiki/Kandi_Burruss "Kandi Burruss")

-   [BWP (group)](https://en.wikipedia.org/wiki/BWP_(group) "BWP (group)")

### **C**

-   [Lady Cam](https://en.wikipedia.org/wiki/Lady_Cam "Lady Cam")

-   [Brooke Candy](https://en.wikipedia.org/wiki/Brooke_Candy "Brooke Candy")

-   [Cardi B](https://en.wikipedia.org/wiki/Cardi_B "Cardi B")

-   [Colette Carr](https://en.wikipedia.org/wiki/Colette_Carr "Colette Carr")

-   [Cha Cha (rapper)](https://en.wikipedia.org/wiki/Cha_Cha_(rapper) "Cha Cha (rapper)")

-   [La Chat](https://en.wikipedia.org/wiki/La_Chat "La Chat")

-   [Choice (rapper)](https://en.wikipedia.org/wiki/Choice_(rapper) "Choice (rapper)")

-   [La Goony Chonga](https://en.wikipedia.org/wiki/La_Goony_Chonga "La Goony Chonga")

-   [Chanel West Coast](https://en.wikipedia.org/wiki/Chanel_West_Coast "Chanel West Coast")

-   [The Conscious Daughters](https://en.wikipedia.org/wiki/The_Conscious_Daughters "The Conscious Daughters")

-   [Imani Coppola](https://en.wikipedia.org/wiki/Imani_Coppola "Imani Coppola")

-   [Cupcakke](https://en.wikipedia.org/wiki/Cupcakke "Cupcakke")

### **D**

-   [Kat Dahlia](https://en.wikipedia.org/wiki/Kat_Dahlia "Kat Dahlia")

-   [Deadly Venoms](https://en.wikipedia.org/wiki/Deadly_Venoms "Deadly Venoms")

-   [Wanda Dee](https://en.wikipedia.org/wiki/Wanda_Dee "Wanda Dee")

-   [The Def Dames](https://en.wikipedia.org/wiki/The_Def_Dames "The Def Dames")

-   [Dessa](https://en.wikipedia.org/wiki/Dessa "Dessa")

-   [Dev (singer)](https://en.wikipedia.org/wiki/Dev_(singer) "Dev (singer)")

-   [Diamond the Body](https://en.wikipedia.org/wiki/Diamond_the_Body "Diamond the Body")

-   [Kanary Diamonds](https://en.wikipedia.org/wiki/Kanary_Diamonds "Kanary Diamonds")

-   [Rah Digga](https://en.wikipedia.org/wiki/Rah_Digga "Rah Digga")

-   [Dimples D.](https://en.wikipedia.org/wiki/Dimples_D. "Dimples D.")

-   [Doechii](https://en.wikipedia.org/wiki/Doechii "Doechii")

-   [Asian Doll](https://en.wikipedia.org/wiki/Asian_Doll "Asian Doll")

-   [Kash Doll](https://en.wikipedia.org/wiki/Kash_Doll "Kash Doll")

### **E**

-   [Carmen Electra](https://en.wikipedia.org/wiki/Carmen_Electra "Carmen Electra")

-   [Missy Elliott](https://en.wikipedia.org/wiki/Missy_Elliott "Missy Elliott")

### **F**

-   [Fan 3](https://en.wikipedia.org/wiki/Fan_3 "Fan 3")

-   [Kari Faux](https://en.wikipedia.org/wiki/Kari_Faux "Kari Faux")

-   [Feloni](https://en.wikipedia.org/wiki/Feloni "Feloni")

-   [Fergie (singer)](https://en.wikipedia.org/wiki/Fergie_(singer) "Fergie (singer)")

-   [Tiffany Foxx](https://en.wikipedia.org/wiki/Tiffany_Foxx "Tiffany Foxx")

-   [Njena Reddd Foxxx](https://en.wikipedia.org/wiki/Njena_Reddd_Foxxx "Njena Reddd Foxxx")

-   [Free Marie](https://en.wikipedia.org/wiki/Free_Marie "Free Marie")

-   [Pearl Future](https://en.wikipedia.org/wiki/Pearl_Future "Pearl Future")

-   [Sylk-E. Fyne](https://en.wikipedia.org/wiki/Sylk-E._Fyne "Sylk-E. Fyne")

### **G**

-   [Hurricane G](https://en.wikipedia.org/wiki/Hurricane_G "Hurricane G")

-   [Heather B. Gardner](https://en.wikipedia.org/wiki/Heather_B._Gardner "Heather B. Gardner")

-   [Geneva (singer)](https://en.wikipedia.org/wiki/Geneva_(singer) "Geneva (singer)")

-   [The Get Em Mamis](https://en.wikipedia.org/wiki/The_Get_Em_Mamis "The Get Em Mamis")

-   [GloRilla](https://en.wikipedia.org/wiki/GloRilla "GloRilla")

-   [Cat Glover](https://en.wikipedia.org/wiki/Cat_Glover "Cat Glover")

-   [Janine Gordon](https://en.wikipedia.org/wiki/Janine_Gordon "Janine Gordon")

-   [Katie Got Bandz](https://en.wikipedia.org/wiki/Katie_Got_Bandz "Katie Got Bandz")

-   [Rappin' Granny](https://en.wikipedia.org/wiki/Rappin%27_Granny "Rappin' Granny")

-   [Gripsta](https://en.wikipedia.org/wiki/Gripsta "Gripsta")

### **H**

-   [Sasha Go Hard](https://en.wikipedia.org/wiki/Sasha_Go_Hard "Sasha Go Hard")

-   [Tina Harris](https://en.wikipedia.org/wiki/Tina_Harris "Tina Harris")

-   [Mona Haydar](https://en.wikipedia.org/wiki/Mona_Haydar "Mona Haydar")

-   [Kalyn Heffernan](https://en.wikipedia.org/wiki/Kalyn_Heffernan "Kalyn Heffernan")

-   [Qveen Herby](https://en.wikipedia.org/wiki/Qveen_Herby "Qveen Herby")

-   [Alaya High](https://en.wikipedia.org/wiki/Alaya_High "Alaya High")

-   [Lauryn Hill](https://en.wikipedia.org/wiki/Lauryn_Hill "Lauryn Hill")

-   [Hopie](https://en.wikipedia.org/wiki/Hopie "Hopie")

-   [Angela Hunte](https://en.wikipedia.org/wiki/Angela_Hunte "Angela Hunte")

-   [Heather Hunter](https://en.wikipedia.org/wiki/Heather_Hunter "Heather Hunter")

-   [HWA (group)](https://en.wikipedia.org/wiki/HWA_(group) "HWA (group)")

### **I**

-   [Ice Spice](https://en.wikipedia.org/wiki/Ice_Spice "Ice Spice")

-   [Icy Blu](https://en.wikipedia.org/wiki/Icy_Blu "Icy Blu")

-   [II Tru](https://en.wikipedia.org/wiki/II_Tru "II Tru")

-   [Lady iLe](https://en.wikipedia.org/wiki/Lady_iLe "Lady iLe")

-   [India (actress)](https://en.wikipedia.org/wiki/India_(actress) "India (actress)")

### **J**

-   [J. J. Fad](https://en.wikipedia.org/wiki/J._J._Fad "J. J. Fad")

-   [Ms. Jade](https://en.wikipedia.org/wiki/Ms._Jade "Ms. Jade")

-   [Jaz (musician)](https://en.wikipedia.org/wiki/Jaz_(musician) "Jaz (musician)")

-   [Jessi (musician)](https://en.wikipedia.org/wiki/Jessi_(musician) "Jessi (musician)")

-   [Lia Marie Johnson](https://en.wikipedia.org/wiki/Lia_Marie_Johnson "Lia Marie Johnson")

-   [Toya Johnson](https://en.wikipedia.org/wiki/Toya_Johnson "Toya Johnson")

-   [Ta'Rhonda Jones](https://en.wikipedia.org/wiki/Ta%27Rhonda_Jones "Ta'Rhonda Jones")

-   [Junglepussy](https://en.wikipedia.org/wiki/Junglepussy "Junglepussy")

### **K**

-   [K-Swift](https://en.wikipedia.org/wiki/K-Swift "K-Swift")

-   [K. P. & Envyi](https://en.wikipedia.org/wiki/K._P._%26_Envyi "K. P. & Envyi")

-   [K.Flay](https://en.wikipedia.org/wiki/K.Flay "K.Flay")

-   [Kamaiyah](https://en.wikipedia.org/wiki/Kamaiyah "Kamaiyah")

-   [KaMillion](https://en.wikipedia.org/wiki/KaMillion "KaMillion")

-   [Kesha](https://en.wikipedia.org/wiki/Kesha "Kesha")

-   [Khia](https://en.wikipedia.org/wiki/Khia "Khia")

-   [Euna Kim](https://en.wikipedia.org/wiki/Euna_Kim "Euna Kim")

-   [Kitty (rapper)](https://en.wikipedia.org/wiki/Kitty_(rapper) "Kitty (rapper)")

-   [Kreayshawn](https://en.wikipedia.org/wiki/Kreayshawn "Kreayshawn")

-   [L'Trimm](https://en.wikipedia.org/wiki/L%27Trimm "L'Trimm")

-   [Lady B](https://en.wikipedia.org/wiki/Lady_B "Lady B")

-   [Lady Luck (rapper)](https://en.wikipedia.org/wiki/Lady_Luck_(rapper) "Lady Luck (rapper)")

-   [The Lady of Rage](https://en.wikipedia.org/wiki/The_Lady_of_Rage "The Lady of Rage")

-   [Queen Latifah](https://en.wikipedia.org/wiki/Queen_Latifah "Queen Latifah")

-   [Latto](https://en.wikipedia.org/wiki/Latto "Latto")

-   [Mélange Lavonne](https://en.wikipedia.org/wiki/M%C3%A9lange_Lavonne "Mélange Lavonne")

-   [HeeSun Lee](https://en.wikipedia.org/wiki/HeeSun_Lee "HeeSun Lee")

-   [Lega-C](https://en.wikipedia.org/wiki/Lega-C "Lega-C")

-   [Leikeli47](https://en.wikipedia.org/wiki/Leikeli47 "Leikeli47")

-   [Coi Leray](https://en.wikipedia.org/wiki/Coi_Leray "Coi Leray")

-   [Lil Debbie](https://en.wikipedia.org/wiki/Lil_Debbie "Lil Debbie")

-   [Lil' Kim](https://en.wikipedia.org/wiki/Lil%27_Kim "Lil' Kim")

-   [Lisa Lisa](https://en.wikipedia.org/wiki/Lisa_Lisa "Lisa Lisa")

-   [Amber Liu (singer)](https://en.wikipedia.org/wiki/Amber_Liu_(singer) "Amber Liu (singer)")

-   [Lizzo](https://en.wikipedia.org/wiki/Lizzo "Lizzo")

-   [Dej Loaf](https://en.wikipedia.org/wiki/Dej_Loaf "Dej Loaf")

-   [Lisa Lopes](https://en.wikipedia.org/wiki/Lisa_Lopes "Lisa Lopes")

-   [Lumidee](https://en.wikipedia.org/wiki/Lumidee "Lumidee")

-   [MC Lyte](https://en.wikipedia.org/wiki/MC_Lyte "MC Lyte")

### **M**

-   [Remy Ma](https://en.wikipedia.org/wiki/Remy_Ma "Remy Ma")

-   [Kellee Maize](https://en.wikipedia.org/wiki/Kellee_Maize "Kellee Maize")

-   [Mala Reignz](https://en.wikipedia.org/wiki/Mala_Reignz "Mala Reignz")

-   [Mapei (rapper)](https://en.wikipedia.org/wiki/Mapei_(rapper) "Mapei (rapper)")

-   [Lil Mariko](https://en.wikipedia.org/wiki/Lil_Mariko "Lil Mariko")

-   [Angie Martinez](https://en.wikipedia.org/wiki/Angie_Martinez "Angie Martinez")

-   [Marvaless](https://en.wikipedia.org/wiki/Marvaless "Marvaless")

-   [Katherine McAlpine](https://en.wikipedia.org/wiki/Katherine_McAlpine "Katherine McAlpine")

-   [Daisha McBride](https://en.wikipedia.org/wiki/Daisha_McBride "Daisha McBride")

-   [Megan Thee Stallion](https://en.wikipedia.org/wiki/Megan_Thee_Stallion "Megan Thee Stallion")

-   [Ms. Melodie](https://en.wikipedia.org/wiki/Ms._Melodie "Ms. Melodie")

-   [Menajahtwa](https://en.wikipedia.org/wiki/Menajahtwa "Menajahtwa")

-   [Mia X](https://en.wikipedia.org/wiki/Mia_X "Mia X")

-   [Christina Milian](https://en.wikipedia.org/wiki/Christina_Milian "Christina Milian")

-   [Miss Ko](https://en.wikipedia.org/wiki/Miss_Ko "Miss Ko")

-   [MISSPSTAR](https://en.wikipedia.org/wiki/MISSPSTAR "MISSPSTAR")

-   [Monaleo](https://en.wikipedia.org/wiki/Monaleo "Monaleo")

-   [Tay Money](https://en.wikipedia.org/wiki/Tay_Money "Tay Money")

-   [LoLa Monroe](https://en.wikipedia.org/wiki/LoLa_Monroe "LoLa Monroe")

-   [Georgia Anne Muldrow](https://en.wikipedia.org/wiki/Georgia_Anne_Muldrow "Georgia Anne Muldrow")

-   [Kaila Mullady](https://en.wikipedia.org/wiki/Kaila_Mullady "Kaila Mullady")

### **N**

-   [Akua Naru](https://en.wikipedia.org/wiki/Akua_Naru "Akua Naru")

-   [Naturi Naughton](https://en.wikipedia.org/wiki/Naturi_Naughton "Naturi Naughton")

-   [Nikki D](https://en.wikipedia.org/wiki/Nikki_D "Nikki D")

-   [Nonchalant](https://en.wikipedia.org/wiki/Nonchalant "Nonchalant")

### **O**

-   [Oaktown's 357](https://en.wikipedia.org/wiki/Oaktown%27s_357 "Oaktown's 357")

-   [OMB Bloodbath](https://en.wikipedia.org/wiki/OMB_Bloodbath "OMB Bloodbath")

-   [Overweight Pooch](https://en.wikipedia.org/wiki/Overweight_Pooch "Overweight Pooch")

### **P**

-   [Passion (rapper)](https://en.wikipedia.org/wiki/Passion_(rapper) "Passion (rapper)")

-   [Penny (rapper)](https://en.wikipedia.org/wiki/Penny_(rapper) "Penny (rapper)")

-   [Pepa (rapper)](https://en.wikipedia.org/wiki/Pepa_(rapper) "Pepa (rapper)")

-   [Jackie Hill Perry](https://en.wikipedia.org/wiki/Jackie_Hill_Perry "Jackie Hill Perry")

-   [Whitney Peyton](https://en.wikipedia.org/wiki/Whitney_Peyton "Whitney Peyton")

-   [Prima J](https://en.wikipedia.org/wiki/Prima_J "Prima J")

-   [Princess Superstar](https://en.wikipedia.org/wiki/Princess_Superstar "Princess Superstar")

-   [Hesta Prynn](https://en.wikipedia.org/wiki/Hesta_Prynn "Hesta Prynn")

-   [Psalm One](https://en.wikipedia.org/wiki/Psalm_One "Psalm One")

-   [PTAF](https://en.wikipedia.org/wiki/PTAF "PTAF")

### **Q**

-   [Queen Pen](https://en.wikipedia.org/wiki/Queen_Pen "Queen Pen")

### **R**

-   [Audra the Rapper](https://en.wikipedia.org/wiki/Audra_the_Rapper "Audra the Rapper")

-   [Rapsody](https://en.wikipedia.org/wiki/Rapsody "Rapsody")

-   [Rasheeda](https://en.wikipedia.org/wiki/Rasheeda "Rasheeda")

-   [The Real Roxanne](https://en.wikipedia.org/wiki/The_Real_Roxanne "The Real Roxanne")

-   [Natina Reed](https://en.wikipedia.org/wiki/Natina_Reed "Natina Reed")

-   [Lakeyah](https://en.wikipedia.org/wiki/Lakeyah "Lakeyah")

-   [Rubi Rose](https://en.wikipedia.org/wiki/Rubi_Rose "Rubi Rose")

-   [MC Router](https://en.wikipedia.org/wiki/MC_Router "MC Router")

-   [Renni Rucci](https://en.wikipedia.org/wiki/Renni_Rucci "Renni Rucci")

-   [Rye Rye](https://en.wikipedia.org/wiki/Rye_Rye "Rye Rye")

### **S**

-   [Sa-Roc](https://en.wikipedia.org/wiki/Sa-Roc "Sa-Roc")

-   [Salt (rapper)](https://en.wikipedia.org/wiki/Salt_(rapper) "Salt (rapper)")

-   [Sammus](https://en.wikipedia.org/wiki/Sammus "Sammus")

-   [Sarai (rapper)](https://en.wikipedia.org/wiki/Sarai_(rapper) "Sarai (rapper)")

-   [Saweetie](https://en.wikipedia.org/wiki/Saweetie "Saweetie")

-   [Nitty Scott](https://en.wikipedia.org/wiki/Nitty_Scott "Nitty Scott")

-   [Amanda Seales](https://en.wikipedia.org/wiki/Amanda_Seales "Amanda Seales")

-   [The Sequence](https://en.wikipedia.org/wiki/The_Sequence "The Sequence")

-   [Sha-Rock](https://en.wikipedia.org/wiki/Sha-Rock "Sha-Rock")

-   [Otep Shamaya](https://en.wikipedia.org/wiki/Otep_Shamaya "Otep Shamaya")

-   [Kodie Shane](https://en.wikipedia.org/wiki/Kodie_Shane "Kodie Shane")

-   [Roxanne Shante](https://en.wikipedia.org/wiki/Roxanne_Shante "Roxanne Shante")

-   [Sharaya J](https://en.wikipedia.org/wiki/Sharaya_J "Sharaya J")

-   [Shawnna](https://en.wikipedia.org/wiki/Shawnna "Shawnna")

-   [Magnolia Shorty](https://en.wikipedia.org/wiki/Magnolia_Shorty "Magnolia Shorty")

-   [Shunda K](https://en.wikipedia.org/wiki/Shunda_K "Shunda K")

-   [Natalie Sims](https://en.wikipedia.org/wiki/Natalie_Sims "Natalie Sims")

-   [Sirah (rapper)](https://en.wikipedia.org/wiki/Sirah_(rapper) "Sirah (rapper)")

-   [Kid Sister](https://en.wikipedia.org/wiki/Kid_Sister "Kid Sister")

-   [Siya](https://en.wikipedia.org/wiki/Siya "Siya")

-   [Smooth (singer)](https://en.wikipedia.org/wiki/Smooth_(singer) "Smooth (singer)")

-   [Snow Tha Product](https://en.wikipedia.org/wiki/Snow_Tha_Product "Snow Tha Product")

-   [Jasmine Solano](https://en.wikipedia.org/wiki/Jasmine_Solano "Jasmine Solano")

-   Antoinette

-   Asian Doll

-   Azealia Banks

-   Awkwafina

## **B**

-   Bhad Bhabie

-   BigKlit

-   Bonnie Blue

-   Boss

-   Bbymutha

-   bktherula

-   The Buttress

-   Blactina

## **C**

-   Conscious Daughters

-   Comaneci

-   Chastain Stone

-   Cardi B

-   Cuban Doll

-   Chelly The Mc

-   CupcakKe

-   Cuzzxo

-   Coi Leray

## **D**

-   Doja Cat

-   Da Brat

-   Dick Rydah

-   Dej Loaf

## **E**

-   Evidenc3 (Montreal rapper)

## **F**

-   Foxy Brown

-   Flo Milli

-   Fmc Kellss

## **G**

-   Gavlyn

## **H**

-   Holly Hood ProE

-   <https://open.spotify.com/artist/7s738bnlRDsdvb8nTcuWbB>

-   Honey G

## **I**

-   Iggy Azalea

## **J**

-   Jacki-O (female rapper)

-   Jah Jah (female rapper)

-   Jentina (female rapper) *England*

-   Jewelz (female rapper)

-   Jayla (female rapper)

-   Jayla Marie 🔥🔥🔥🔥🔥🔥

## **K**

-   K-Swift

-   Kana (Finnish musician)

-   Kat Dahlia (female rapper) [Kat Dahlia - Gangsta](http://www.youtube.com/watch?v=trtdEg34eII)

-   Keko

-   Kesha

-   Khia

-   KennK

-   Kid Sister

-   Kitty (female rapper)

-   Kitty Kat

-   [Killa Kim (female rapper)](https://hiphopdatabase.fandom.com/wiki/Killa_Kim_(female_rapper) "Killa Kim (female rapper)")

-   Kreayshawn

-   Kytami

## **L**

-   Lady of Rage

-   Lauryn Hill

-   Lil Kim

-   Lil Mama

-   Lil Debbie

-   Lil Kymchii

-   Littyfromdacity

-   Londynn B

-   Lumidee (female rapper) [Lumidee - Never Leave You (Uh Oh)](http://www.youtube.com/watch?v=TBGUFzGnsII)

-   Lil Tay

-   Little Simz

-   Left-Eye

## **M**

-   [Makiin (female rapper)](https://hiphopdatabase.fandom.com/wiki/Makiin_(female_rapper) "Makiin (female rapper)")

-   Mia X

-   Missy Elliott

-   MC Lyte

-   Ms. Toi

-   [Monalisa (female rapper)](https://hiphopdatabase.fandom.com/wiki/Monalisa_(female_rapper) "Monalisa (female rapper)")

-   Monate Q

-   Monie Love

-   Mulatto

-   Medusa

-   Megan Thee Stallion

## **N**

-   Nefertiti

-   Nikki D.

-   Noni Zondi (female rapper)

-   Nicki Minaj

-   Nitty Scott

## **O**

-   

## **P**

-   Porche' 9-11

-   PoppinCid

[Porche' 9-11](http://www.soundcloud.com/porche9-11)

## **Q**

-   Q-Tee (female rapper)

-   Queen Latifah (female rapper)

-   Queen Pen (female rapper)

-   Queen Cookie

-   Qveen Herby

## **R**

-   Remy Ma

-   [Raqula](https://hiphopdatabase.fandom.com/wiki/Lanse_Base_(Blazed_Out_Party_Rap_w/female_rapper)) (female rapper)

-   Reema Major

-   Ree-Ree a.k.a Dj Lolli-Pop Ria (Dj, Female Emcee)

-   [Ruby (female rapper)](https://hiphopdatabase.fandom.com/wiki/Ruby_(female_rapper) "Ruby (female rapper)")

-   Roscoe

-   Rapsody

-   Rico Nasty

-   Renni Ricci (female rapper)

-   Rubi Rose

-   Rah Digga

## **S**

-   Snow Tha Product

-   Saweetie

-   SmokeHijabi

-   SANDRINETTE

-   Silk Tymes Leather

-   Storm(Outlawz)

-   Shine Brida

-   Spicegurlpurp

## **T**

-   Tally

## **U**

-   UptownTrinn

## **V**

-   V-Nasty

## **W**

-   Woahhvicky

## **X**

-   

## **Y**

-   Yolandi Visser

-   Young M.A

-   Yo-Yo
